\section{Method}
\label{sec:method}

\subsection{Loss-conditional formulation}

A standard PINN \citep{raissi2019} approximates the solution of a
single PDE $F u = 0$ with auxiliary boundary, initial, and (optionally)
data conditions $\{B u = g_B,\, I u = g_I,\, D u = g_D\}$ by minimising
the weighted composite loss
\begin{equation}
   \mathcal{L}^{\mathrm{PINN}}(\theta;\, w) =
     w_F \,\| F u_\theta \|_{L^2}^2 +
     w_B \,\| B u_\theta - g_B \|_{L^2}^2 +
     w_I \,\| I u_\theta - g_I \|_{L^2}^2 +
     w_D \,\| D u_\theta - g_D \|_{L^2}^2 ,
\label{eq:standard-pinn}
\end{equation}
in the network parameters~$\theta$. The choice
$w = (w_F, w_B, w_I, w_D)$ controls a strong tradeoff between
satisfying the residual and matching the auxiliary constraints; in
practice the weights are tuned by grid search or by an adaptive
schedule (SA-PINN \citep{mcclenny2020}, ReLoBRaLo \citep{bischof2021},
Causal-PINN \citep{wang2024}).

We replace the fixed-$w$ problem with a \emph{family} of problems
indexed by a parameter vector $\lambda \in \Lambda$, where
$\Lambda \subseteq \mathbb{R}^{d_\lambda}$ is either (i) the set of
admissible loss weights itself
($\lambda = w$, $d_\lambda = 4$ for Burgers and BL), or (ii) a
physical parameter of the PDE such as a wavenumber or mobility ratio
($\lambda = k$, $d_\lambda = 1$ for Helmholtz). The
\emph{loss-conditional} PINN (LC-PINN) is a single network
\begin{equation}
   u_\theta : \Omega \times \Lambda \to \mathbb{R},
\qquad
   (x, \lambda) \mapsto u_\theta(x, \lambda),
\label{eq:lc-network}
\end{equation}
trained to minimise the $\lambda$-expectation of the per-instance loss,
\begin{equation}
   J(\theta) = \mathbb{E}_{\lambda \sim p_\lambda}\!\left[
       \mathcal{L}\bigl(\lambda;\, u_\theta(\cdot, \lambda)\bigr)
   \right] ,
\label{eq:lc-objective}
\end{equation}
where $p_\lambda$ is a fixed sampling distribution (uniform on
$\Lambda$ unless stated otherwise). The architectural cost is one
extra input of width $d_\lambda$ at the first layer; the per-step
compute is one forward/backward pass at a freshly drawn~$\lambda$.
This generalises the loss-conditional networks of
\citet{dosovitskiy2020} from generative loss-mixture amortisation
to the residual-loss setting in which the ``loss mixture'' is the
PDE residual itself.

\subsection{Inference: $K$-shot averaging across $\lambda$}
\label{sec:k-shot}

At evaluation time we report a single rel-$L^2$ error per task. For
the loss-weight conditioning case there is no canonical ``true''
weight, so following \citet{dosovitskiy2020} we average network
predictions over $K$ samples of $\lambda$ drawn from~$p_\lambda$:
\begin{equation}
   \hat u(x) = \frac{1}{K}\sum_{i=1}^{K} u_\theta(x, \lambda^{(i)}),
   \qquad \lambda^{(i)} \stackrel{\text{i.i.d.}}{\sim} p_\lambda .
\label{eq:k-shot}
\end{equation}
This $K$-shot averaging exposes the variance structure of the
LC-PINN across the loss-weight family and underpins the amortisation
analysis in \Cref{sec:results}: a baseline PINN must be retrained
$K$ times to produce $K$ predictions; the LC-PINN produces all $K$
from a single training run.

\subsection{$\lambda$-invariance at the LC optimum}

\input{sections/theorem}

\subsection{Network and training details}
\label{sec:training-details}

All experiments use a fully-connected $\tanh$ network with hidden
widths $[64, 64, 64, 64]$, Xavier initialisation, and a single
real-valued output head. Two conditioning routes are used: in the
\emph{loss-weight} mode (Burgers, BL) $\lambda$ is concatenated to
the spatial--temporal coordinates at the input layer following
\citet{dosovitskiy2020}; in the \emph{parametric-coefficient} mode
(Helmholtz 1D/2D/3D, Schrödinger) $\lambda$ is mapped to FiLM
\citep{perez2018film} scale/shift parameters that modulate every
hidden layer, followed by an L-BFGS finishing pass with a
revert-on-worse safety check. The FiLM+L-BFGS combination is what
buys the order-of-magnitude lift over plain concat in the
parametric-coefficient mode (\Cref{sec:appendix-film-loss-weight}
documents both directions). Training uses Adam
($\eta = 10^{-3}$) with cosine annealing and gradient-norm clipping
at~$1.0$; each step samples $\lambda \sim p_\lambda$ and evaluates
the per-instance loss at the current batch of collocation points.
$\lambda$ is normalised to $[-1, 1]$ before entering the network.
Implementation: PyTorch~2.9 on Apple~M4 Max via the MPS backend.
Full hyperparameters and per-equation collocation budgets are listed
in \Cref{sec:appendix-hyper}.
